% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

\name{Jin Zheyu\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{  Male, 24\\Nationality: China\\Email: kimcherwoo@gmail.com\\Mobile: (+82)010-8301-0173 \\Work: (+82)02-2194-5187}
\address{  Nexstreaming Corporation \\  2nd Flr, Gwangseong Bldg, \\ 831-47Yeoksamdong Gangnam-gu \\Seoul, South Korea.\\Postcode: 135-080 }
% semes this is comment???     


\begin{resume}
 
\section{Objective}  Master of Computer Science. 

\section{Education} {\bf Bachelor of Engineering  } \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                Beijing Institute of Technology (BIT), Beijing, China,  2010 	\\
                Major: Software Engineering \\
                GPA: 3.3/4.0
 
\section{Employment} 
				{ \bf Software Engineer} \hfill October 2010 - Present \\
                Platform 1 Team, Nexstreaming Corporation, Seoul, South Korea               
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Ported embedded NexPlayer to various Samsung and LG android devices.
                \item   Developed NexPlayer Hardware SDK, which utilizes Android devices' built-in video and audio decoder.
				\item   Developed NexPlayer SDK verification server and client(Servlet,Tomcat,Mysql,JSON used), gained AWS expierence.
                \end{itemize}
 
                {\bf Assistant Analyst} (intern)\hfill            April 2010 - May 2010 \\
                Department of Business Analysis, Baidu Inc., Beijing, China. 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Analyzed business model, income structure and marketing strategy of target companies.
                 \end{itemize} 

 \section{Language \\ Skills} 
				{\bf English:} TOEFL IBT 105(Reading26, Listening 28, Speaking 24, Writing 27)\\
				{\bf Chinese:} native \\
				{\bf Korean: } native	\\	 
 
 \section{Leadership \\ Involvement} 
				{ \bf Leader of an amateur soccer team of 20 people.} \hfill August 2011 - Present \\           
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Arranged training and match schedules, and managed team fund. 
                \item  Learned and practiced various communication skills and ways to implement my decisions.
                \end{itemize}

\section{Research \\ Activities} 
				{ \bf Leader of Robocup 2D simulation team.} \hfill August 2009 - December 2009 \\  								
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Developed a Robocup 2D simulation team for Robocup ChinaOpen2009 with a group of peers. 
                \item  Learned basic knowledge of Artificial Intelligence and how to lead peers toward a common goal.
                \end{itemize}

\section{Extra-Curricular \\ Activities} 
				{ \bf Volunteer of 2008 Beijing Olympic.} \hfill July 2008 - August 2008 \\  		
                 Did a good job as assistant manager of Press Conference Room in Wukesong Basket Ball Stadium.
 
 \section{Professional \\ Skills} {\sl Languages :} C/C++, Java, Python, GO, C\#, PHP \\
                {\sl Operating Systems:} Linux, Windows.
 
\section{Honors and Awards }             
             {\it 3rd Place in Robocup ChinaOpen2009}, 	December	2009 \\             			
			 {\it Renmin Scholarship of BIT(3rd class)}, January	2009 \\            	
			 {\it Renmin Scholarship of BIT(3rd class)}, September	2008 \\            
			 {\it Renmin Scholarship of BIT(3rd class)}, January	2008 \\            
			 {\it Renmin Scholarship of BIT(2nd class)}, September	2007 \\  
			 {\it Renmin Scholarship of BIT(3rd class)}, January	2007 			 			 
\end{resume}
\end{document}